Species richness destabilizes trophic communities in freshwater ecosystems

### 2020-03-10 manuscript/bef_stability/manuscript.Rmd
New stab indirect effect computation, to be tested rigourously
Add introduction bullet points + indirect effect of bm + mv fig 1 to 2

---
title: Species richness destabilizes trophic communities in freshwater ecosystems
author: Alain Danet, Maud Mouchet, Elisa Thébault and Colin Fontaine
date: \today 
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
bibliography: references.bib
---

@@

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

@@

@@

- Fishing operations and station
  - kept one protocol type by station
  - kept one sampling operation per year (of the season the most sampled in the
    time series)
  - remove operations which sampling effort (length of river) superior to average
    plus or minus 30% of sd (by station)
  - kept station that had 10 or more samplings, i.e. followed 10 years or more

@@

- 7 Resource nodes:
  - based on diet database

@@

@@

pca_rotated <- compute_rotated_pca(
  .data = pca_pressure[, !names(pca_pressure) %in% "station"],
  naxis = 5 
)

@@

$$
\Log_{10}(S_i) = \beta_0 + \beta_R\Log_{10}(x_{Ri}) + \epsilon_{ij}
$$

$$
S_i = 10^(\beta_0 + \beta_R\Log_{10}(x_{Ri}) + \epsilon_{ij})
$$

$$
S_i = 10^(\beta_0) \times 10^(\beta_R\Log(x_{Ri})) \times 10^(\epsilon_{ij})
$$

$$
S_i = 10^(\beta_{0}) \times x_{Ri}10^(\beta_{R}) \times 10^(\epsilon_{ij})
$$

@@

SEM enables to reason in terms of causal relationship between components. The
goal was to understand the mechanisms behind the negative relationship biomass
stability and species richness and the positive relationship between total
biomass and species richness.

@@

The community structure was characterized by total species richness (TSR),
species turnover (ST), median average weighted trophic level (TLvl) and median connectance.
Total species richness was the number of unique fish species that were observed
at a given station over the whole sampling. Species turnover was computed as average
dissimilarity between the different community composition through time. The
dissimilarity was calculated on species presence/absence with the Bray-Curtis
method implemented in the `vegan` R package (`vegdist` function). Both median
connectance and Tlvl were just computed as the median over the temporal period.
For the details of the computation of the trophic networks, see Network
inference part.

@@

---
# Environment to community attributes and stability  
---
We linked environmental variables both to community structure and stability
components. Rooted in assembly theory, environment filters species that can
establish in a community and thus affect community structure. (+ add specific
hypothesis about physical and climate). (1) We hypothesized that enrichment
(characterized by DBO) and mean annual temperature will increase ST
[@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
decrease biomass stability directly without going by community structure. First,
instability of habitat and environmental factors may in turn drive biomass
instability [@hansen_climate_2013]. Secondly, average environmental conditions
such as enrichment can increase directly CV by increasing species biomass
fluctuations [@tabi_warming_2019]. Increasing temperature was also hypothesized
to decrease stability through starvation resulting from high metabolic activity
[@tabi_warming_2019].

---
# Species richness to community attributes 
---
To reveal the mechanisms behind the relationship between species richness and
biomass stability, causal links were set from species richness to other
community attributes. (4) We hypothesized that TSR increased ST because
increasing species richness because of assembly processes. Species rich
communities are more resistant to invasion and thus increase ST
[@tilman_niche_2004; @shurin_how_2007]. (5) We hypothesized also that TSR
decreased connectance following results from @thebault_stability_2010;
@winemiller_must_1989. But theoretically, some ecological networks can show the
inverse relationship [@winemiller_must_1989]. (6) We hypothesized also that TSR
will modulate average weighted trophic level because of food web assembly
processes. If *TSR increased and that new species are placed at random in the
network, we expected a positive relationship between Tlvl and TSR because
individuals of the higher trophic level have a higher body mass [to think
again]*. Finally, we set up causal relationships from community attributes to
stability components.

---
#  Community attributes to stability
---
We hypothesized that (7) TSR decreased synchrony between species by portfolio
effects [REF] and increased $\overline{CV_{sp}}$ [@tilman_biodiversity_2006] *to
complete*. We hypothesized that (8) ST increased $\overline{CV_{sp}}$ and that it
decreased synchrony. (9a) We expected that Tlvl had a positive or negative
relationship with synchrony, bottom-up effects should result in positive whereas
top-down in negative relationship. We expected a (9b) negative relationship
between Tlvl and $\overline{CV_{sp}}$ if predators stabilised population
fluctuations or if the increasing part of biomass in the predators decreased
$\overline{CV_{sp}}$ because of their higher body mass (if mean increase faster than
variance). (10a) Connectance was expected to decrease or increase $\overline{CV_{sp}}$
and (10b) synchrony because of top down effects or bottom up effects.

@@

```{r get-sem-coeff}
total_effect_stab_sem <- compute_stab_sem_indirect(sem = stab_sem_rich,
  p_val_thl = 0.05)

total_effect_bm_sem <- compute_bm_sem_indirect(sem = bm_sem_rich,
  p_val_thl = 0.05)

coef_stab_sem <- coef(stab_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)

@@

# get coeff
coef_stab_tlvl <- map(list(stab = stab_tlvl_mod), fixed.effects)

@@

## Contradictory responses of species richness on total biomass and biomass stability

```{r}
richness_lab <- "Total richness (Log 10)"
stab_lab <- "Biomass stability (Log 10)"
bm_lab <- "Total biomass (Log 10)"
```

```{r p-s-div}
lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
lim_log_rich_tot <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich_tot")
# Plot left

@@

---
# Total biomass versus TSR
---
TSR increased total biomass (`r b_co_r`% `r b_ci_r` by 1% TSR increase). Total
biomass was `r b_co_t`% `r b_ci_t` higher in the high than in the low trophic group. However,
the increase of total biomass with the increase of TSR was lower in the high
than the low trophic group (`r b_co_r_t3`% `r b_ci_r_t3` and `r b_co_r_t2`%
`rb_ci_r_t2` respectively,  by 1% TSR increase).
---
# Stability versus TSR
---
However, biomass stability decreased with TSR (`r s_co_r`% `r s_ci_r` by 1%
TSR increase). Biomass stability was overall `r s_co_t`% `r s_ci_t` higher for the high
than the low trophic group. But biomass stability decreased by `r s_co_r_t3`% by
1% increase in TSR in the high trophic group and increased by `r s_co_r_t2`% `r s_ci_r_t2`
in the low trophic group.

```{r sem-plot, fig.dim = c(10,10)}
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple
to_plot <- c(1, 6, 7)

plot_grid(
  plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
      ncol = length(to_plot), labels = LETTERS[1]),
  plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[2:3], rel_widths = c(.6, .4)),
  ncol = 1,
  rel_heights = c(.4, .6)
)
```

```{r}
total_effect_bm_sem
total_effect_stab_sem
```

---
# Total biomass
---
We found that the primary drivers of total biomass were the total species
richness (TSR) and the average trophic level (Tlvl) ($r_\delta = 0.35$ and
$r_\delta = 0.40$ resp.) whereas connectance had no significant effect  (Fig.
\@ref{fig:sem-plot} C). The stream size had a direct positive effect on total
biomass ($r_\delta = 0.22$) whereas CV of flow and avg DBO increased total
biomass ($r_\delta = - 0.2$). Avg temperature, CV of river size and CV of DBO
had no direct effects on total biomass.

TSR had also a indirect positive effect on total biomass through Tlvl ($r_\delta
= 0.21$), that is, TSR had a total positive effect of $0.56$ on total biomass.
The stream size had a total effect on total biomass as strong as TSR ($r_\delta
= 0.54$), indirectly through Tlvl ($r_\delta = 0.10$) and TSR ($r_\delta = 0.22$).
The avg temperature of the river had an indirect positive effect on total biomass
($r_\delta = 0.48$), through Tlvl ($r_\delta = 0.11$) and TSR ($r_\delta = 0.33$).
Avg DBO, CV DBO and CV of river size had no or weak indirect effect on total
biomass.

---
# Biomass stability
---
\overline{CV_{sp}} ($r_\delta = -1.26$) decreased biomass stability more than
synchrony ($r_\delta = -0.55$, Figure \@ref{fig:sem-plot}). TSR had a strong
positive effect on \overline{CV_{sp}} and a strong negative effect on synchrony
whereas Tlvl and connectance had no significant effects on either
\overline{CV_{sp}} nor synchrony. The avg river size had a small positive direct
effect on synchrony ($r_\delta = 0.19$). The other environmental variables had
no significant direct effects on \overline{CV_{sp}} nor synchrony.

Indirectly through synchrony and \overline{CV_{sp}}, TSR had a total negative
effect on biomass stability ($r_\delta = -0.26$). Avg river size and avg
temperature had also a total effect which was negative on biomass stability
(resp. $r_\delta = -0.24$ and $r_\delta = -0.16$), going through richness 
(resp. $r_\delta = -0.10$ and $r_\delta = -0.16$).

@@

We tested for the first time the determinants of temporal biomass stability in a
foodweb with an empirical dataset at such high temporal and spatial scales.

@@

---
# Effect of synchrony and cv_sp  
---
It was unexpected that the average population CV had a stronger negative effect
on biomass stability than synchrony [@bluthgen_land_2016;
@olivier_independent_nodate] *cf ref in bluthgen*. We see two hypothesis that
can raise this effect. First, the opportunity for diet differentiation can be
low in streams compare to other organisms. Bird species are for example quite
specialized in seed, flying or soil arthropods or mammals which gives
opportunities for independent dynamics. Plants also can achieve independent
dynamics either spatial segregation, niche differentiation. Because fish
species even piscivorous one are quite opportunistic in
their foraging. Secondly, in trophic network, amplitude of species biomass
involved in trophic interactions could covary positively TOTHINKABOUT.

---
# Effect of trophic level and connectance are richness effects:
---
Our path analysis reveled that, although species richness has a strong effect on
connectance and the average trophic level, network structure had itself little
to no effect either on synchrony nor average population stability. This result
contradicts precedent theoretical studies on the relationship
between stability and network structure [@angelis_stability_1975, @may_will_1972], although
they considered different stability metrics (i.e. local stability of equilibrium
point). The reason might be that in our inferred network, network structure is
strongly constraints by assembly processes. Indeed, connectance decreased with
increasing species richness [@thebault_stability_2010], because a small fraction
of links are realized because of food diet constraints. In theoretical studies,
connectance can be tuned from 0 (no links) to 1 (all possible links are
present). SAMEFORTLVL
Finally, the biomass stability of freshwater ecosystems can be derived by
species richness because, through trophic structure constraints, species
richness determine largely network structure.

@@

>>>>

---
title: Species richness destabilizes trophic communities in freshwater ecosystems
author: Alain Danet, Maud Mouchet, Elisa Thébault and Colin Fontaine
date: \today 
output:
  pdf_document:
      fig_caption: true
bibliography: references.bib
---

@@

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "total_sem_effect.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

@@

- Diversity - stability and diversity - biomass / productivity
  - well studied: both experimentally, empirically and theoretically
  - mecanisms:
    - stability: insurance (asynchrony),
    - diversity: overyielding (complementarity)
  - key papers: [@tilman_biodiversity_2006, @loreau_species_2008,
    @thibaut_understanding_2013, @may_will_1972]
  - BUT: less vertical diversity, trophic communities

- Vertical diversity and stability/biomass
  - well studied: theoretically and (experimentally, less)
  - mecanisms:
    - stability: top-down and bottom-up effect
    - biomass: top-down and bottom-up effects (pyramids of biomass)
  - key papers:[@barbier_pyramids_2019, @shanafelt_david_w._stability_nodate]
  - BUT: local stability, little systems

- Environment can drive stability and biomass:
  - forcing: environmental forcing on communities 
  - can lead to misleading effect: @grace_integrative_2016

- Big scope assessment:
  - inconsistency between theoretical and empirical stability
    - theoretical: no cv_sp nor synchrony
  - No studies on stability-richness in empirical trophic communities
    - no effect of trophic structure

- Goal: Assess relation biomass/stability-diversity in empirical trophic communities
  - introduce effect of trophic structure and environment
  - merge gap between theoretical and empirical studies

- What we have done:
  - big empirical dataset
  - rebuilding empirical network
  - assess relationship between environment, community structure and stability

@@

- Fishing operations and station
  - kept one protocol type by station
  - kept one sampling operation per year (of the season the most sampled in the
    time series)
  - remove operations which sampling effort (length of river sampled) superior to average
    plus or minus 30% of sd (by station)
  - kept station that had 10 or more samplings, i.e. followed 10 years or more

@@

- 7 Resource nodes:
  - based on diet database
  - no information about their biomass

- Size class:
  - quantile: 9 size class per species

- Interaction:
  - Fish-resources and resources: based on diet data 
  - Fish-fish:
    1. diet data: is piscivorous?
    2. allometric relationship: predation range from .03 to .45 of body size

@@

- Collected during fishing operation:   
  - River size (width and depth)
  - Altitude and slope
  - distance to source
- Independant dataset from naiades: 
  - flow, temperature, DBO
    1. moving window average
    2. annual average 
    3. interpolation along rivers (OpenStars + SSN package)

@@

pca_rotated <- compute_rotated_pca(
  .data = pca_pressure[, !names(pca_pressure) %in% "station"],
  naxis = 5 
)
```

@@

$$
\begin{align}

\log_{10}S_i &= \beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}\\

S_i &= 10^{\beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}}\\

S_i &= 10^{\beta_0} \times 10^{\beta_R\log_{10}x_{Ri}} \times
10^{\epsilon_{ij}}\\

S_i &= 10^{\beta_{0}} \times x_{Ri}10^{\beta_{R}} \times 10^{\epsilon_{ij}}

\end{align}
$$

@@

SEM enables to reason in terms of causal relationship between components. We
aimed to understand the mechanisms behind the negative relationship biomass
stability and species richness and the positive relationship between total
biomass and species richness.

@@

The community structure was characterized by total species richness,
median average weighted trophic level and median connectance.
Total species richness was the number of unique fish species that were observed
at a given station over the whole sampling. Both median
connectance and average trophic level were just computed as the median over the
temporal period. For the details of the computation of the trophic networks,
see Network inference part.

@@

---
# Environment to community attributes and stability  
---
We linked environmental variables both to community structure and stability
components. Rooted in assembly theory, environment filters species that can
establish in a community and thus affect community structure. (+ add specific
hypothesis about physical and climate). (1) We hypothesized that enrichment
(characterized by DBO) and mean annual temperature will increase species turnover
[@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
decrease biomass stability directly without going by community structure. First,
instability of habitat and environmental factors may in turn drive biomass
instability [@hansen_climate_2013]. Secondly, average environmental conditions
such as enrichment can increase directly CV by increasing species biomass
fluctuations [@tabi_warming_2019]. Increasing temperature was also hypothesized
to decrease stability through starvation resulting from high metabolic activity
[@tabi_warming_2019].

---
# Species richness to community attributes 
---
To reveal the mechanisms behind the relationship between species richness and
biomass stability, causal links were set from species richness to other
community attributes. (5) We hypothesized also that species richness
decreased connectance following results from @thebault_stability_2010;
@winemiller_must_1989. But theoretically, some ecological networks can show the
inverse relationship [@winemiller_must_1989]. (6) We hypothesized also that species richness
will modulate average weighted trophic level because of food web assembly
processes. If *species richness increased and that new species are placed at
random in the network, we expected a positive relationship between average
trophic level and species richness because individuals of the higher trophic
level have a higher body mass [to think again]*. Finally, we set up causal
relationships from community attributes to stability components.

---
#  Community attributes to stability
---
We hypothesized that (7) species richness decreased synchrony between species
[REF] and increased $\overline{CV_{sp}}$ [@tilman_biodiversity_2006] *to
complete*. (8a) We expected that average trophic level had a positive or
negative relationship with synchrony, bottom-up effects should result in
positive whereas top-down in negative relationship. We expected a (8b) negative
relationship between average trophic level and $\overline{CV_{sp}}$ if predators
stabilised population
fluctuations or if the increasing part of biomass in the predators decreased
$\overline{CV_{sp}}$ because of their higher body mass (if mean increase faster than
variance). (9a) Connectance was expected to decrease or increase $\overline{CV_{sp}}$
and (9b) synchrony because of top down effects or bottom up effects.

@@

```{r get-sem-coeff}
coef_stab_sem <- coef(stab_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)

@@

# get coeff
coef_stab_tlvl <- map(list(stab = stab_tlvl_mod), fixed.effects)
```

@@

```{r sem-plot, fig.dim = c(10,10), fig.cap = "SEM"}
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple

plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[1:2], rel_widths = c(.55, .45))
```

```{r get-bm-sem-single-effect}
bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)
get_clean_sem_coef <- function(sem = NULL, resp = NULL, pred = NULL) {
  out <- sem[sem$Response == resp & sem$Predictor == pred, ]$Std.Estimate
  out <- ifelse(length(out) == 0, 0, out)
  round(out, 2)
}

rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "log_rich_tot")
tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "t_lvl")
RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "log_RC1")
```

```{r get-bm-tot-effect-env}
bm_all_params <- get_coefficient_piecewisesem(sem = bm_sem_rich, p_val_thl = NULL)

# effect of env on bm 
env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05)
# env on com 
env_on_t_lvl <- get_env_on_com(fit = bm_all_params,
  p_val_thl = 0.05,
  com = "t_lvl")
env_on_ct <- get_env_on_com(fit = bm_all_params,
  p_val_thl = 0.05,
  com = "ct")
env_on_richness <- get_env_on_rich(fit = bm_all_params,
  p_val_thl = 0.05)
```

```{r get-sem-tot-effect-rich}
rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05)
rich_on_sync <- get_rich_on_bm_comp(fit = bm_all_params,
  p_val_thl = 0.05,
  bm_comp = "log_sync")
rich_on_cv_sp <- get_rich_on_bm_comp(fit = bm_all_params,
  p_val_thl = 0.05,
  bm_comp = "log_cv_sp")
```

---
# Total biomass
---

Species richness and the average trophic level were the main direct drivers of
total biomass ($r_\delta = `r rich_on_bm`$ and $r_\delta = `r tlvl_on_bm`$ resp.) whereas
connectance had no significant effect (Fig. \@ref(fig:sem-plot) C). The stream
size had a direct positive effect on total biomass ($r_\delta = `r RC1_on_bm`$) whereas
avg temperature, avg DBO, CV of river size and CV of DBO had no direct effects
on total biomass.

Species richness had also a indirect positive effect on total biomass through
average trophic level, species richness had a total positive effect of $`r rich_on_bm`$
on total biomass. The stream size had a total effect on total biomass as strong
as species richness ($r_\delta =`r env_on_bm["log_RC1"]`$), indirectly through average trophic level
and species richness. The avg temperature of the river had an indirect positive
effect on total biomass ($r_\delta = `r env_on_bm["log_RC2"]`$), through
average trophic level and species richness as well. Avg DBO, CV DBO and CV of
river size had no or weak indirect effect on total biomass
(resp. $r_\delta =`r env_on_bm["log_RC3"]`$, $r_\delta =`r env_on_bm["log_RC5"]`$, $r_\delta =`r env_on_bm["log_RC4"]`$).

```{r get-sem-single-effect}
stab_sem_coef <- filter(coef_stab_sem, P.Value < 0.05)
get_clean_sem_coef <- function(sem = NULL, resp = NULL, pred = NULL) {
  out <- sem[sem$Response == resp & sem$Predictor == pred, ]$Std.Estimate
  out <- ifelse(length(out) == 0, 0, out)
  round(out, 2)
}

sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab", pred = "log_sync")
cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab", pred = "log_cv_sp")
RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
```

```{r get-sem-tot-effect-env}
all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
# effect of env on stab

env_on_stab <- get_env_on_stab(fit = all_params, p_val_thl = 0.05)
# effect of env on sync and cv_sp
env_on_sync <- get_env_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync")
env_on_cv_sp <- get_env_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp")
# env on com 
env_on_t_lvl <- get_env_on_com(fit = all_params,
  p_val_thl = 0.05,
  com = "t_lvl")
env_on_ct <- get_env_on_com(fit = all_params,
  p_val_thl = 0.05,
  com = "ct")
env_on_richness <- get_env_on_rich(fit = all_params,
  p_val_thl = 0.05)
```

```{r get-sem-tot-effect-rich}
rich_on_stab <- get_rich_on_stab(fit = all_params,
  p_val_thl = 0.05)
rich_on_sync <- get_rich_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync")
rich_on_cv_sp <- get_rich_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp")
```

---
# Biomass stability
---

\overline{CV_{sp}} ($r_\delta = `r cv_sp_on_stab`$) decreased biomass stability more than
synchrony ($r_\delta = `r sync_on_stab`$, Figure \@ref(fig:sem-plot)). Species richness had a strong
positive effect on \overline{CV_{sp}} and a strong negative effect on synchrony
whereas average trophic level and connectance had no significant effects on either
\overline{CV_{sp}} nor synchrony. The avg river size had a small positive direct
effect on synchrony ($r_\delta = `r RC1_on_sync`$). The other environmental variables had
no significant direct effects on either \overline{CV_{sp}} nor synchrony.

Indirectly through synchrony and \overline{CV_{sp}}, species richness had a total negative
effect on biomass stability ($r_\delta = `r rich_on_stab`$). Avg river size and avg
temperature had also a total effect which was negative on biomass stability
(resp. $r_\delta = `r env_on_stab["log_RC1"]`$ and $r_\delta = `r env_on_stab["log_RC2"]`$),
going through richness (resp. $r_\delta = `r env_on_richness["log_RC1"]`$ and
$r_\delta = `r env_on_richness["log_RC2"]`$).

## Species richness increases total biomass but decreases biomass stability

```{r}
richness_lab <- "Total richness (Log 10)"
stab_lab <- "Biomass stability (Log 10)"
bm_lab <- "Total biomass (Log 10)"

stab_div_caption <- paste0("Relationship between biomass stability (log 10) (top panel) or total biomass (log 10) (bottom panel) versus total species richness.") 
```

```{r p-s-div, fig.cap = stab_div_caption}
lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
lim_log_rich_tot <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich_tot")
# Plot left

@@

---
# Total biomass versus species richness
---
species richness increased total biomass (`r b_co_r`% `r b_ci_r` by 1% species richness increase). Total
biomass was `r b_co_t`% `r b_ci_t` higher in the high than in the low trophic
group. However, the increase of total biomass with the increase of species
richness was lower in the high than the low trophic group (`r b_co_r_t3`% `r
b_ci_r_t3` and `r b_co_r_t2`% `r b_ci_r_t2` respectively,  by 1% species
richness increase).

---
# Stability versus species richness
---

However, biomass stability decreased with species richness (`r s_co_r`% `r s_ci_r` by 1%
species richness increase). Biomass stability was overall `r s_co_t`% `r s_ci_t` higher for the high
than the low trophic group. But biomass stability decreased by `r s_co_r_t3`% by
1% increase in species richness in the high trophic group and increased by `r s_co_r_t2`% `r s_ci_r_t2`
in the low trophic group.

@@

For the first time, we assessed the determinants of total biomass and temporal
biomass stability in empirical trophic communities at such high temporal and
spatial scales. We showed that species richness increased total biomass but 
decreased biomass stability. In particular, species richness decreased
synchrony and increased species CV ($\LaTeX$). Surprisingly, the avg trophic
level and connectance had no effects on either synchrony nor species CV.
Finally, we showed that high trophic group was more stable than low trophic
group but that high trophic was responsible for the negative stability-diversity
relationship.

@@

The total effect of river size on biomass stability was as negative as species richness,
indicating that big rivers had a high negative effect on stability.

---
# Effect of synchrony and cv_sp  
---

It was unexpected that the average population CV had a stronger negative effect
on biomass stability than synchrony [@bluthgen_land_2016;
@olivier_independent_nodate] *cf ref in bluthgen*. We see two hypothesis that
can raise this effect. First, the opportunity for diet differentiation can be
low in streams compare to other organisms. Bird species are for example quite
specialized in seed, flying or soil arthropods or mammals which gives
opportunities for independent dynamics. Plants also can achieve independent
dynamics either spatial segregation, niche differentiation. Because fish
species even piscivorous one are quite opportunistic in
their foraging. Secondly, in trophic network, amplitude of species biomass
involved in trophic interactions could covary positively TOTHINKABOUT.

---
# Effect of trophic level and connectance are richness effects:
---

Our path analysis revealed that, although species richness has a strong effect on
connectance and the average trophic level, network structure had itself little
to no effect either on synchrony nor average population stability. This result
contradicts precedent theoretical studies on the relationship
between stability and network structure [@angelis_stability_1975, @may_will_1972], although
they considered different stability metrics (i.e. local stability of equilibrium
point). The reason might be that in our inferred network, network structure is
strongly constraints by assembly processes. Indeed, connectance decreased with
increasing species richness [@winemiller_must_1989, @thebault_stability_2010],
because a small fraction of links are realized because of food diet constraints.
In theoretical studies, connectance can be tuned from 0 (no links) to 1 (all
possible links are present) [@angelis_stability_1975]. SAMEFORTLVL
Finally, the biomass stability of freshwater ecosystems can be derived by
species richness because, through trophic structure constraints, species
richness determine largely network structure.

@@

## PCA of environmental variables

```{r}
prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
  map_dbl(., ~round(.x * 100))

tot_var_expl_pca <- round(sum(pca_rotated$rotated$Vaccounted["Proportion Var", ]) * 100)

pca_caption <- paste0(
  "Rotated axis of PCA on environmental variables. The five components
  explained,", tot_var_expl_pca, "% of the variance (",
  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
  "(A) Axis 1 was positively related to the river size, axis 2 was related to
  average temperature and negatively related to the river slope and altitude.
  (B) Axis 3 was negatively related to the CV of flow and average enrichment.
  Axis 4 was related to the CV of river size. Finally, axis 5 was related to the
  CV of enrichment.")
```

```{r pca-rotated, fig.cap = pca_caption}
to_plot <- c(1, 6, 7)
plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
  ncol = length(to_plot), labels = LETTERS[1:3])
```
